Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-07-22 paper/current/main.tex

We find that the length of the vector captures the connection diversity of the organization compare to its size. The length of the vector is correlated with the number of connections to other organizations divided by the number of researchers, which can be interpreted as connection diversity compared to their size. This suggests that researchers in the organization with a long vector have less freedom to move to other organizations compare to their size while researchers in the organization with short vector have more freedom to move. This observation can also be related to the organization's strategy. Most prestigious universities have policies that can enhance their collaboration with other organizations such as visiting program, giving additional affiliation to the researcher. We also show a correlation between the length of the vector and various organization-level factors such as diverse rankings,  amount of the funding, number of doctorates granted (Fig.~\ref{fig:supp:length_vs_metaInfo}), indicating the length of the organization vector capture diverse characteristics of the organization.

>>>>

We find that the length of the vector captures the connection diversity of the organization compare to its size. The length of the vector is correlated with the number of connections to other organizations divided by the number of researchers, which can be interpreted as connection diversity compared to their size (Fig.~\ref{fig:length}b, inset). This suggests that researchers in the organization with a long vector have less freedom to move to other organizations compare to their size while researchers in the organization with short vector have more freedom to move. This observation can also be related to the organization's strategy. Most prestigious universities have policies that can enhance their collaboration with other organizations such as visiting program, giving additional affiliation to the researcher. We also show a correlation between the length of the vector and various organization-level factors such as diverse rankings,  amount of the funding, number of doctorates granted (Fig.~\ref{fig:supp:length_vs_metaInfo}), indicating the length of the organization vector capture diverse characteristics of the organization.
